\Large{All in the family:\\Anna and Lisa Hahner's finishing times in\\the 2016 women's Olympic marathon}

### 2017-02-03 paper/paper.tex
description of simulation histograms

We can observe from the results of the simulations in Figure \ref{fig:simdiff} that if Anna and Lisa had run independently of each other, they would have rarely finished simultaneously.  We see that Anna and Lisa finished within 30 seconds of each other in less than 300 of the 10,000 simulated races.  And they finished in consecutive rank in less than 175 of the 10,000 races.  Therefore, the close finish that we observed would be very unlikely if we were to believe the twins raced independently of each other.

@@

>>>>

@@

A histogram of the differences between Anna and Lisa's simulated finishes can be found in Figure \ref{fig:simdiff}.  The first plot shows the distribution of the absolute differences in time.  Differences are grouped in 30 second bins along the x-axis and the count for each bin is denoted by the vertical length of bar along the y-axis.  The second plot shows the distribution of the absolute differences in ranking.  Differences are grouped as single units ranging from no runner between the twins to nearly 120 runners between them.

The results plotted in the histograms question the credibility of Anna and Lisa's story.  The results suggest that  a simultaneous finish would be very rare if Anna and Lisa had run independently of each other.  For example, in less than 300 of the 10,000 simulated races did Anna and Lisa finished within 30 seconds of each other .  And they finished in consecutive rank in less than 175 of the 10,000 races.  Therefore, the close finish that we observed, where Anna and Lisa crossed the finish line one-after-the-other, would be very unlikely if we were to believe the twins raced independently of each other.

The results holds even if you replace their personal best time with their time halfway through the race.  While this reduces the variation in the predicted outcome of each runner and, therefore, reduces the expected distance between Anna and Lisa, it is still quite rare for Anna and Lisa to finish simultaneously or consecutively.
